\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\newcolumntype{C}[1]{>{\centering}p{#1}}
\newcolumntype{L}[1]{>{\raggedleft}p{#1}}
\small
\begin{tabularx}{\textwidth}{L{\firstColWidth{}}|C{\secondColWidth{}}|X}
\toprule
{\bf RPM Package Name} & {\bf Version} & {\bf Info/URL}  \\
\midrule

% <-- begin entry for R
R-gnu12-ohpc &
\multirow{2}{*}{4.2.1} &
\multirow{3}{\linewidth}{R is a language and environment for statistical computing and graphics (S-Plus like). \newline {\color{logoblue} \url{http://www.r-project.org}}}\\
R-gnu13-ohpc &
& \\
\cline{1-2} R-gnu14-ohpc &\multirow{1}{*}{4.4.1}
& \\
\hline
% <-- end entry for R

% <-- begin entry for cubelib
cubelib-gnu14-ohpc &
\multirow{1}{*}{4.8.2} &
\multirow{1}{\linewidth}{CUBE Uniform Behavioral Encoding generic presentation library component.  {\color{logoblue} \url{http://www.scalasca.org/software/cube-4.x/download.html}}}\\
\hline
% <-- end entry for cubelib

% <-- begin entry for gsl
gsl-gnu12-ohpc &
\multirow{3}{*}{2.7.1} &
\multirow{3}{\linewidth}{GNU Scientific Library (GSL). \newline {\color{logoblue} \url{http://www.gnu.org/software/gsl}}}\\
gsl-gnu13-ohpc &
& \\
gsl-gnu14-ohpc &
& \\
\hline
% <-- end entry for gsl

% <-- begin entry for metis
metis-gnu12-ohpc &
\multirow{3}{*}{5.1.0} &
\multirow{3}{\linewidth}{Serial Graph Partitioning and Fill-reducing Matrix Ordering. \newline {\color{logoblue} \url{http://glaros.dtc.umn.edu/gkhome/metis/metis/overview}}}\\
metis-gnu13-ohpc &
& \\
metis-gnu14-ohpc &
& \\
\hline
% <-- end entry for metis

% <-- begin entry for openblas
openblas-gnu12-ohpc &
\multirow{2}{*}{0.3.21} &
\multirow{3}{\linewidth}{An optimized BLAS library based on GotoBLAS2. \newline {\color{logoblue} \url{http://www.openblas.net}}}\\
openblas-gnu13-ohpc &
& \\
\cline{1-2} openblas-gnu14-ohpc &\multirow{1}{*}{0.3.28}
& \\
\hline
% <-- end entry for openblas

% <-- begin entry for opari2
opari2-gnu14-ohpc &
\multirow{1}{*}{2.0.8} &
\multirow{1}{\linewidth}{An OpenMP runtime performance measurement instrumenter. \newline {\color{logoblue} \url{https://www.vi-hps.org/projects/score-p}}}\\
\hline
% <-- end entry for opari2

% <-- begin entry for plasma
plasma-gnu12-ohpc &
\multirow{3}{*}{21.8.29} &
\multirow{3}{\linewidth}{Parallel Linear Algebra Software for Multicore Architectures. \newline {\color{logoblue} \url{https://icl.utk.edu/plasma/overview/index.html}}}\\
plasma-gnu13-ohpc &
& \\
plasma-gnu14-ohpc &
& \\
\hline
% <-- end entry for plasma

% <-- begin entry for scotch
scotch-gnu12-ohpc &
\multirow{3}{*}{6.0.6} &
\multirow{3}{\linewidth}{Graph, mesh and hypergraph partitioning library. \newline {\color{logoblue} \url{http://www.labri.fr/perso/pelegrin/scotch}}}\\
scotch-gnu13-ohpc &
& \\
scotch-gnu14-ohpc &
& \\
\hline
% <-- end entry for scotch

% <-- begin entry for superlu
superlu-gnu12-ohpc &
\multirow{2}{*}{5.2.1} &
\multirow{3}{\linewidth}{A general purpose library for the direct solution of linear equations. \newline {\color{logoblue} \url{http://crd.lbl.gov/~xiaoye/SuperLU}}}\\
superlu-gnu13-ohpc &
& \\
\cline{1-2} superlu-gnu14-ohpc &\multirow{1}{*}{7.0.0}
& \\
\hline
% <-- end entry for superlu

\bottomrule
\end{tabularx}
